%!TEX root = report.tex
Drivers in California already have to share their roads with a few of the self-driving cars that are being tested there. It will not be long before autonomous cars are ubiquitous. One might wonder how these changes in traffic influence the flow of traffic. A lot of research has been done on how one might regulate traffic differently given that most or all of the cars are autonomous. However this research generally proposes changes in infrastructure, and then models the influence of changing the ratio of autonomous cars versus human drivers. This paper focusses on the question of how adding autonomous cars to `normal traffic' without changing the infrastructure influences the flow of traffic. Before discussing our model and our results we first introduce the current state of the art in \cref{sub:intro:state_of_the_art} and further expand the contribution of this paper in \cref{sub:intro:new_idea}.

\subsection{State of the Art}
\label{sub:intro:state_of_the_art}
\textcite{dresner2007sharing} propose a hybrid intersection control mechanism that allows for both human and autonomous drivers. This proposal is a follow-up of several earlier papers, primarily their earlier paper, \cite{dresner2005traffic}. In this paper they propose a new infrastructure for autonomous intersection management which uses a multi-agent reservation system, consisting of two types of agents: the intersection managers and the driver agents. The intersection managers each manage an intersection, and are responsible for directing the driver agents through their intersection. The driver agents control their vehicles and communicate with intersection managers to get through intersections safely. The intersection managers have an intersection control policy, which they use to determine if the space to pass through requested by a driver agent is free at that time. If so, they confirm the reservation, and if not, they decline. This system was shown to work well and decrease traffic delays. 

% new idea
However, they found that while system described above works well when all agents in the simulation are autonomous, it is not yet applicable to the real world, since currently hardly any vehicles are autonomous. To solve this problem they looked into different policies concerning combining autonomous vehicles with human driven vehicles. In this hybrid system human drivers used the traffic lights, and self-driving cars used the reservation system described above.

% results
\textcite{dresner2007sharing} showed that some of the policies also resulted in a decrease of delays in traffic. The largest decrease was found when the autonomous vehicle to human ratio was high, however the self-driving car in this scenario encountered significantly less delays than their human driven counterpart due their use of the reservation system.

% relevance
A future with self-driving cars is becoming more realistic. To fully benefit from the emergence of autonomous vehicles our traffic system should aim to use their high-precision abilities to create more efficient, fast, and safe auto transportation.


\subsection{New Idea}
\label{sub:intro:new_idea}	
\algemeen{Eerste zin is iets verbeterd, maar kan nog steeds beter of anders.}
Where \textcite{dresner2007sharing} alter every intersection and every vehicle, we propose to change nothing in the existing infrastructure and look at whether the presence of autonomous cars by themselves can make a difference in traffic delays and crashes. 

\later{Updaten als we meer fancy shit in ons model hebben.}
We model several traffic situations where both self-driving cars and `normal' cars are part of the traffic using a simple intersection, without any of the extra infrastructure proposed by earlier research. 

% We start with a simple intersection where normal traffic rules apply. As we are further along in the project we will add more complex situations such as traffic lights and stop signals. Furthermore we might also look into different acceleration speeds for the `normal' cars and different drivers such as those proposed by \textcite{paruchuri2002multi}, or cars with (adaptive) cruise control.

Our model of autonomous cars is loosely based \textcite{jiang2010microscopic}, our human drivers are based on \textcite{paruchuri2002multi}.

\algemeen{Moet hier dan de verwachtte resultaten?}

This text is organised as follows: the next section discusses the model and our experiment in detail. \Cref{sec:results} presents and discusses the results of our experiment and \cref{sec:conclusion} concludes the paper with the implications of our results.