\documentclass[a4paper]{article}

\usepackage[english]{babel}

% References
\usepackage[backend=bibtex]{biblatex}
\usepackage{csquotes}
\bibliography{biblio}

\title{Project Plan\\ \sc{traffic simulation self-driving cars}}
\author{%
	Laura van de Braak (s2165341) \and 
	Jelmer van der Linde (s1772791) \and 
	Laura Baakman (s1869140)
}

\begin{document}

\maketitle

\paragraph{Problem} How will self driving cars change traffic?
\paragraph{State of the art} \citeauthor{paruchuri2002multi} describe an agent simulation of unorganised traffic, and \citeauthor{jiang2010microscopic} a simulation of autonomous drivers. \citeauthor{paruchuri2002multi} discuss a number of factors that play a part in how a driver reacts to traffic. Human drivers are imperfect, and can be distracted or influenced by external or internal factors. Alternatively, \citeauthor{jiang2010microscopic} describe how one can model autonomous vehicles.
\paragraph{New idea} We model severl traffic situations where both self-driving cars and `normal' cars are part of the traffic. We will start out with a simple intersection where the normal rules apply. After which we will add more complex situations such as traffic lights, stop signs. Furthermore we might also look into different acceleration speeds for the `normal' cars and different drivers such as those proposed by \citeauthor{paruchuri2002multi}.
\paragraph{Results} We expect that a high ratio of self-driving cars will result in fewer traffic jams, but that adding some self-driving cars will not change the flow of traffic significantly.  
\paragraph{Relevance} Self-driving cars are becoming more and more prevalent. Several companies are already testing their self-driving cars on the Californian streets \cite{honda}. These cars will change the flow of traffic. 

\printbibliography

\end{document}